Tropical Andes Functional diversity for plants and Frugivores

### 2024-05-14 code/L2/L2_1_TropicalAndes_funcdiv.Rmd
read in site location key files from L1, update extent, reorder more code

```{r}
# objects for functional diversity
PAM_plant_site_final <- readRDS(file = file.path(data_path_L1,"PAM_plant_site_final.rds"))
PAM_frugivore_site_final <- readRDS(file = file.path(data_path_L1,"PAM_frugivore_site_final.rds"))
plant_traits_df_final <- readRDS(file = file.path(data_path_L1,"plant_traits_df_final.rds"))
frugivore_traits_df_final <- readRDS(file = file.path(data_path_L1,"frugivore_traits_df_final.rds"))
```

@@

@@

@@

#Get functional dispersion
fdis_frugivore <- alpha_fd_indices_frugivore$functional_diversity_indices$fdis

@@

@@

@@

#Get functional dispersion
fdis_plant <- alpha_fd_indices_plant$functional_diversity_indices$fdis

@@

@@

# Functional diversity plots

## Project FD objects
```{r}
# set crs of sf objects
#spatial_fdis_plant <- spatial_fdis_plant %>% st_set_crs(4326)
spatial_fdis_frugivore <- spatial_fdis_frugivore %>% st_set_crs(4326)
```

```{r}
#spatial_fdis_plant_projected <- st_transform(spatial_fdis_plant, 5389)
spatial_fdis_frugivore_projected <- st_transform(spatial_fdis_frugivore, 5389)
```

```{r}
# Raster to raster point
#spec_FD_raster_plant_point <- rasterToPoints(fd_raster_plant, spatial = TRUE)
spec_FD_raster_frugivore_point <- rasterToPoints(fd_raster_frugivore, spatial = TRUE)
# Convert to a 'conventional' dataframe
#fd_raster_plant_point <- data.frame(spec_FD_raster_plant_point)
fd_raster_frugivore_point <- data.frame(spec_FD_raster_frugivore_point)
```

```{r}
plantgridFDTA <-
  ggplot() +
  geom_sf(data = worldMap, fill = "white")+
  geom_sf(data = TApoly, fill = "grey", size = 0.1) +
  geom_tile(data= fd_raster_plant_point, aes(x=x, y=y, fill=fdis_plant)) +
  scale_fill_scico(palette = "romaO", direction = 1) +
  coord_sf(xlim = c(-85, -54), ylim = c(-24, 14), expand = FALSE) +
  theme(
    plot.background = element_rect(fill = "#f1f2f3"),
    panel.background = element_rect(fill = "lightblue"),
    panel.grid = element_blank(),
    line = element_blank(),
    rect = element_blank()
  ) +
  annotation_scale(location = "bl", width_hint = 0.5) +
  annotation_north_arrow(location = "bl", which_north = "true", 
  pad_x = unit(0.3, "in"), pad_y = unit(0.3, "in"), style = north_arrow_fancy_orienteering) +
  labs(title = "Tropical Andes Plant Functional Dispersion", x = "Longitude", y = "Latitude", fill = "FD")
plantgridFDTA
```

```{r}
frugivoregridFDTA <-
  ggplot() +
  geom_sf(data = worldMap, fill = "white")+
  geom_sf(data = TApoly, fill = "grey", size = 0.1) +
  geom_tile(data= fd_raster_frugivore_point, aes(x=x, y=y, fill=fdis_frugivore)) +
  scale_fill_scico(palette = "romaO", direction = 1) +
  coord_sf(xlim = c(-85, -60), ylim = c(-24, 14), expand = FALSE) +
  theme(
    plot.background = element_rect(fill = "#f1f2f3"),
    panel.background = element_rect(fill = "lightblue"),
    panel.grid = element_blank(),
    line = element_blank(),
    rect = element_blank()
  ) +
  annotation_scale(location = "bl", width_hint = 0.5) +
  annotation_north_arrow(location = "bl", which_north = "true", 
  pad_x = unit(0.3, "in"), pad_y = unit(0.3, "in"), style = north_arrow_fancy_orienteering) +
  labs(title = "Tropical Andes Frugivore Functional Dispersion", x = "Longitude", y = "Latitude", fill = "FD")
frugivoregridFDTA
```

>>>>

```{r}
# objects for functional diversity
PAM_plant_site_final <- readRDS(file = file.path(data_path_L1,"PAM_plant_site_final.rds"))
PAM_frugivore_site_final <- readRDS(file = file.path(data_path_L1,"PAM_frugivore_site_final.rds"))
plant_traits_df_final <- readRDS(file = file.path(data_path_L1,"plant_traits_df_final.rds"))
frugivore_traits_df_final <- readRDS(file = file.path(data_path_L1,"frugivore_traits_df_final.rds"))
site_loc_key_plant <- readRDS(file = file.path(data_path_L1,"site_loc_key_plant.rds"))
site_loc_key_frugivore <- readRDS(file = file.path(data_path_L1,"site_loc_key_frugivore.rds"))
```

@@

```{r}
# Get functional dispersion
fdis_frugivore <- alpha_fd_indices_frugivore$functional_diversity_indices$fdis
```

@@

```{r}
# Create an empty raster with desired resolution and extent
resolution <- c(0.75, 0.75)  # Set the desired resolution
extent <- c(-85, 60, -24, 14)  # Set the desired extent
empty_raster <- raster(resolution = resolution, xmn = extent[1], xmx = extent[2], ymn = extent[3], ymx = extent[4])
```

@@

@@

## Project FD objects
```{r}
# set crs of sf objects
spatial_fdis_frugivore <- spatial_fdis_frugivore %>% st_set_crs(4326)
```

```{r}
spatial_fdis_frugivore_projected <- st_transform(spatial_fdis_frugivore, 5389)
```

```{r}
# Raster to raster point
spec_FD_raster_frugivore_point <- rasterToPoints(fd_raster_frugivore, spatial = TRUE)
# Convert to dataframe
fd_raster_frugivore_point <- data.frame(spec_FD_raster_frugivore_point)
```

```{r}
frugivoregridFDTA <-
  ggplot() +
  geom_sf(data = Americas, fill = "white")+
  geom_sf(data = TApoly, fill = "grey", size = 0.1) +
  geom_tile(data= fd_raster_frugivore_point, aes(x=x, y=y, fill=fdis_frugivore)) +
  scale_fill_scico(palette = "romaO", direction = 1) +
  coord_sf(xlim = c(-82, -60), ylim = c(-24, 14), expand = FALSE) +
  theme(
    plot.background = element_rect(fill = "#f1f2f3"),
    panel.background = element_rect(fill = "lightblue"),
    panel.grid = element_blank(),
    line = element_blank(),
    rect = element_blank()
  ) +
  annotation_scale(location = "bl", width_hint = 0.5) +
  labs(title = "Tropical Andes Frugivore Functional Dispersion", x = "Longitude", y = "Latitude", fill = "FD")
frugivoregridFDTA
```

@@

```{r}
#Get functional dispersion
fdis_plant <- alpha_fd_indices_plant$functional_diversity_indices$fdis
```

@@

@@

## Project FD objects
```{r}
# set crs of sf objects
spatial_fdis_plant <- spatial_fdis_plant %>% st_set_crs(4326)
```

```{r}
spatial_fdis_plant_projected <- st_transform(spatial_fdis_plant, 5389)
```

```{r}
# Raster to raster point
spec_FD_raster_plant_point <- rasterToPoints(fd_raster_plant, spatial = TRUE)
# Convert to a 'conventional' dataframe
fd_raster_plant_point <- data.frame(spec_FD_raster_plant_point)
```

```{r}
plantgridFDTA <-
  ggplot() +
  geom_sf(data = Americas, fill = "white")+
  geom_sf(data = TApoly, fill = "grey", size = 0.1) +
  geom_tile(data= fd_raster_plant_point, aes(x=x, y=y, fill=fdis_plant)) +
  scale_fill_scico(palette = "romaO", direction = 1) +
  coord_sf(xlim = c(-85, -54), ylim = c(-24, 14), expand = FALSE) +
  theme(
    plot.background = element_rect(fill = "#f1f2f3"),
    panel.background = element_rect(fill = "lightblue"),
    panel.grid = element_blank(),
    line = element_blank(),
    rect = element_blank()
  ) +
  annotation_scale(location = "bl", width_hint = 0.5) +
  annotation_north_arrow(location = "bl", which_north = "true", 
  pad_x = unit(0.3, "in"), pad_y = unit(0.3, "in"), style = north_arrow_fancy_orienteering) +
  labs(title = "Tropical Andes Plant Functional Dispersion", x = "Longitude", y = "Latitude", fill = "FD")
plantgridFDTA
```

@@
